Refractory anaphylaxis: Data from the European Anaphylaxis Registry

### 2018-11-22 analysis/paper/paper.Rmd
changed the README

The data show that drugs more frequently elicited refractory anaphylaxis (`r elicitorTab["drugs","percent"]`% of cases, p < 0.0001) compared to other severe anaphylaxis cases (`r elicitorTab["drugs","percANA"]`%).  Cases elicited by insects (n = `r sum(v$casesInsect)`) were more often due to bees than wasps in refractory cases (`r 5/8*100`% vs `r round(449/(77+1607+4+9+170+3+449)*100,1)`%, p = `r fisher.test(matrix(c(449,5,77+1607+4+9+170+3,3),nrow=2))$p.value %>% round(3)`). The refractory cases occurred mostly in a perioperative setting (`r v$perioperative[3]`% vs. `r v$perioperative[2]`, p < 0.0001). Intramuscular adrenaline (as a first line therapy) was administered in `r therapyTab[1,3]`% of refractory cases, whereas in `r therapyTab[2,3]`% of cases it was applied intravenously (significantly more often than in severe anaphylaxis cases: `r therapyTab[2,2]`%, p < 0.0001). Second line treatment options (e.g. vasopression with dopamine, methylene blue, glucagon) were not used at all for the treatment of refractory cases. The mortality rate in refractory anaphylaxis was significantly higher (`r v$mortality[3]`%) than in severe cases (`r v$mortality[2]`%, p < 0.0001).

>>>>

The data show that drugs more frequently elicited refractory anaphylaxis (`r elicitorTab[elicitorTab$Elicitor=="drugs","percent"]`% of cases, p < 0.0001) compared to other severe anaphylaxis cases (`r elicitorTab[elicitorTab$Elicitor=="drugs","percANA"]`%).  Cases elicited by insects (n = `r sum(v$casesInsect)`) were more often due to bees than wasps in refractory cases (`r 5/8*100`% vs `r round(449/(77+1607+4+9+170+3+449)*100,1)`%, p = `r fisher.test(matrix(c(449,5,77+1607+4+9+170+3,3),nrow=2))$p.value %>% round(3)`). The refractory cases occurred mostly in a perioperative setting (`r v$perioperative[3]`% vs. `r v$perioperative[2]`, p < 0.0001). Intramuscular adrenaline (as a first line therapy) was administered in `r therapyTab[1,3]`% of refractory cases, whereas in `r therapyTab[2,3]`% of cases it was applied intravenously (significantly more often than in severe anaphylaxis cases: `r therapyTab[2,2]`%, p < 0.0001). Second line treatment options (e.g. vasopression with dopamine, methylene blue, glucagon) were not used at all for the treatment of refractory cases. The mortality rate in refractory anaphylaxis was significantly higher (`r v$mortality[3]`%) than in severe cases (`r v$mortality[2]`%, p < 0.0001).
